\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I wish to express my deepest gratitude to my supervisor and long-standing mentor, Dr Bernhard Kainz. His dynamic guidance, free of excessive constraints, allowed me to navigate my research path boldly and innovatively. The insightful feedback he patiently provided on my inquiries has been instrumental in this journey. The success of this project and the immense learning it presented would not have been possible without Dr Kainz’s unwavering support.

My heartfelt appreciation extends to my neighbour, knowledgeable colleague, and self-proclaimed “charming” friend, Tiansheng Xu. With his consistent presence and support, Tiansheng has enriched both the challenging and joyful moments throughout my final year, helping make it a truly memorable experience.

I hold a profound respect for my old friend, Michael Wen. As an adept engineer and culinary maestro, Michael has been a fountainhead of fresh perspectives and gourmet delicacies that have only brightened my journey. Having achieved significant success as a UCL graduate, I am confident his academic voyage at Cambridge will be equally triumphant. In the same vein, I sincerely thank all the friends who have stood by me during this endeavour. Your support has been the beacon guiding my way.

Most importantly, I dedicate this achievement to my loving family: my pillars of strength, Yunjia Zhou and Junhua Fan. Their unwavering trust and belief in my abilities are the foundational stones of my success. They have shared my joys, extended their assistance in times of difficulty, and instilled in me a profound sense of self-assurance. My parents’ pride in my accomplishments is my greatest honour. We often quote, ``The last one is the best one,'' and today, I dedicate this final, best victory to them in this very last but important paragraph. This milestone would not have been attainable without their unconditional love and support.
\end{abstract}